---
title: "Computational Reproducibility"
author: "Fred LaPolla"
date: "10/14/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown file

This file, an R Markdown lets you combine plain text, in the white spaces, and code chunks, in the gray. The text is not really code, but can be used to communicate, while the code chunks let you combine the actual analysis you are running alongside the results. This means someone can see exactly what you did to get your results.

To add a chunk either click on the green Insert button and choose R or hit Command + Option + i (Mac) or Ctrl + Alt + i (PC)

```{r}
3+3
```

## Homework

1) Create an R Project to pull this file from GitHub.

(Saved R project in my documents folder with the following name: compreprohw-marilynvasquez3)

2) Please describe one of the ways that Wilson et. al. suggest is a good practice for computational reproducibility and how a tool like R can be used. Write your answer below.

One of the practices that Wilson et. al. described that is essential for computational reproducibility is good data management. Adequate data management, as described in the article, entails saving the raw data (ideally, this file should remain unchanged), backing it up in multiple locations, and thoroughly describing how the data was processed and analyzed. The author also describes the need to generate “tidy data” in order to facilitate analysis and proposes that results should be tabulated in such a way that each column corresponds to a single variable and each row to a single observation. Moreover, Wilson et. al., also describes other aspects of good data management such as keeping data in nonproprietary formats (i.e. using CSV files instead of Excel), coming up with self-explanatory variable names, using a distinct identifier for each data unit across different data tables, and if possible, submitting data to a repository to make it accessible to other scientists.

Overall, R is a good tool for proper data management and computational reproducibility. This program allows us to leave our raw data unchanged, document the steps of our analysis, and save our analysis commands so we can use them on different data sets. Moreover, we can also share our code with other R users and look up what others have done for their analyses. A special feature of R, R projects, even lets us combine our analysis code, data files, and a history file in a single folder, which allows to keep our data and analysis files organized. 

3) Add a code chunk and find the square root of 4 to the 13th power. If you are unsure of what command to use, google it. 

```{r}
sqrt(4^13)
```

4) Push this homework to the GitHub repository for the homework. 





